### 2020-02-25 manuscript/bef_stability/manuscript.Rmd
Sensivity analysis + cba + improve total effect computation

myload(nmds, habitat_pressure, dir = mypath("report"))
myload(op_analysis, dir = mypath("data"))

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "classes"))

# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin
  )
```

@@

coef_bm_sem <- coef(stab_bm_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)
```

>>>>

myload(nmds, habitat_pressure, dir = mypath("report"))
myload(op_analysis, op_analysis_wo_holes, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis_bbb, dest_dir = mypath("data", "classes"))
# Compute sem dataset 
sem_data <- compute_sem_dataset(
  com = com_data[["tps_com"]],
  network = com_data[["tps_net"]],
  hab_press = habitat_pressure,
  sync = com_data[["sync"]],
  nmds = NULL,
  basin = st_basin
  )
```

@@

coef_bm_sem <- coef(bm_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)
```

### 2020-02-25 report/05-stability.Rmd
Sensivity analysis + cba + improve total effect computation

global_med_occ <- occurence_sp_st %>%
  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
  gather(sp, med_occ, everything())

@@

```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)

#library(future)
#plan(multiprocess)
sem_sensivity_data <- list(full = op_analysis, wo_holes = op_analysis_wo_holes, bbb = op_analysis_bbb)
sem_l_data <- furrr::future_map(sem_sensivity_data,
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    sem_fun = compute_stab_sem_rich_beta,
    dest_dir = mypath("data", "species"))
)

sem_results <- map(sem_l_data,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value)

```{r, fig.dim = c(10, 5)}
p_sensitivity_stab_sem <- map(sem_l_data, ggpiecewisesem)
p_sensitivity_stab_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
plot_grid(plotlist = p_sensitivity_stab_sem)
```
```{r}
p_op_analysis_protocol_bbb <- op_analysis_bbb %>%
  group_by(station) %>%
  slice(1) %>%
  ggplot(aes(x = protocol_type)) + 
  geom_histogram(stat ="count") +
  labs(title = "Station bbb")

@@

>>>>

global_med_occ <- occurence_sp_st %>%
  dplyr::summarise_if(is.double, list(~median(., na.rm = TRUE))) %>%
  gather(sp, med_occ, everything())
```

@@

#### Sensivity to dataset

```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset"}
myload(op_analysis, op_analysis_wo_holes, op_analysis_ov, dir = mypath("data"))
myload(biomass_ts_sax, dir = mypath("data"))
op_analysis_bbb <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
op_analysis_cba <- filter(op_analysis, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "cba",]$station)
op_analysis_wo_holes_bbb <- filter(op_analysis_wo_holes, station %in%
  biomass_ts_sax[biomass_ts_sax$sax == "bbb",]$station)
#library(future)
#plan(multiprocess)
#undebug(build_dataset_get_sem_coefficient)
#undebug(compute_community_temporal_analysis)
#undebug(summarise_network_over_time)
myload(network_metrics, dir = mypath("data", "classes"))
sem_sensivity_data <- list(full = op_analysis, cba = op_analysis_cba, bbb = op_analysis_bbb)
sem_stab_l_data <- furrr::future_map(sem_sensivity_data,
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    sem_fun = compute_stab_sem_rich,
    dest_dir = mypath("data", "classes"))
)

# Nb station by dataset 
nb_station <- map_int(sem_sensivity_data, ~length(unique(.x$station)))

sem_stab_results <- map(sem_stab_l_data,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value)

# Reformat
colnames(sem_stab_results) <- str_to_lower(colnames(sem_stab_results))
sem_stab_results %>%
  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
  ggplot(aes(x = r_p, y = std.estimate)) +
  geom_point(aes(color = dataset)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r, fig.dim = c(10, 5)}
p_sensitivity_stab_sem <- map(sem_stab_l_data, ggpiecewisesem)
p_sensitivity_stab_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
plot_grid(plotlist = p_sensitivity_stab_sem)
```

```{r}
sem_bm_l_data <- furrr::future_map(sem_sensivity_data,
  ~build_dataset_get_sem_coefficient(
    .op = .x,
    sem_fun = compute_prod_sem_rich,
    dest_dir = mypath("data", "classes"))
)
sem_bm_results <- map(sem_bm_l_data,
  ~.x$coefficients[-ncol(.x$coefficients)]) %>%
  enframe() %>%
  rename(dataset = name) %>%
  unnest(value)

# Reformat
colnames(sem_bm_results) <- str_to_lower(colnames(sem_bm_results))
sem_bm_results %>%
  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
  ggplot(aes(x = r_p, y = std.estimate)) +
  geom_point(aes(color = dataset)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
p_sensitivity_bm_sem <- map(sem_bm_l_data, ggpiecewisesem)
p_sensitivity_bm_sem %<>% map2(., names(sem_sensivity_data),  ~ .x + labs(title = .y))
plot_grid(plotlist = p_sensitivity_bm_sem)
```

```{r}
p_op_analysis_protocol_bbb <- op_analysis_bbb %>%
  group_by(station) %>%
  slice(1) %>%
  ggplot(aes(x = protocol_type)) + 
  geom_histogram(stat ="count") +
  labs(title = "Station bbb")

@@

```{r sampling-span-stab}
span_sampling <- op_analysis %>%
  group_by(station) %>%
  summarise(span = max(year) - min(year) + 1)

sem_data %>%
  left_join(span_sampling, by = "station") %>%
  ggplot(aes(x = span, y = biomass_stab)) +
  geom_point()
```
